A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-18 tex/codatadp.tex
Minor

To construct a completion of $\Val$, we must choose values for the free variables of $\Val$, $v_{\ec{x}}$ and $v_{\ec{w_3}}$.
The content of set $\mathcal{T}^\M_{v_{\ec{x}}}( \Val )$ is $\alpha$-equivalent to
\[%\begin{array}{c}
\{
\mu x. \const{A}( \mu y. \const{B}( x )),
\mu x. \const{A}( \mu y. \const{B}( y )),
\mu x. \const{B}( x ),
\mu x. \const{C}( \mu y. \const{A}( x )),
\mu x. \const{A}( \mu y. \const{C}( x )),
\mu x. \const{A}( x )
\}
%\end{array}
\]
Say that $\M$ interprets variables in $\Ec$ based on the mapping $\Val$,
for instance, $x$ is interpretted as $\Val \ec{x}$, $y_1$ as $\Val \ec{y_1}$ and so on.
Assigning a value for $v_{\ec{x}}$ that is $\alpha$-equivalent to a value in $\mathcal{T}^\M_{v_{\ec{x}}}( \Val )$
may cause values in the range of $\Val$ to become $\alpha$-equivalent, 
which in turn may cause $\M$ to be inconsistent.
For instance, say we assign $\mu v_{\ec{x}}. \const{B}( v_{\ec{x}} )$ for $v_{\ec{x}}$.
After this substitution, $\Val \ec{y_2}$ is $\mu v_{\ec{y_2}}. \const{B}( \mu v_{\ec{x}}. \const{B}( v_{\ec{x}} ) )$, 
which has normal form $\mu v_{\ec{y_2}}. \const{B}( v_{\ec{y_2}} )$,
which is $\alpha$-equivalent to $\mu v_{\ec{x}}. \const{B}( v_{\ec{x}} )$.
However, this contradicts the disequality $x \not\teq y_2$ in $\Ec$.

Inversely, if the value assigned to $v_{\ec{x}}$ is not $\alpha$-equivalent to any term in $\mathcal{T}^\M_{v_{\ec{x}}}( \Val )$,
then the values in the range of $\Val$ remain distinct.
For instance, we may assign values such as 
$\mu v_{\ec{x}}. \const{C}( v_{\ec{x}} )$,
$\mu v_{\ec{x}}. \const{C}( \mu x_1. \const{A}( x_1) )$, and
$\mu v_{\ec{x}}. \const{B}( \mu x_1. \const{A}( v_{\ec{x}} ) )$
to $v_{\ec{x}}$.
Notice that legal substitutions for $v_{\ec{x}}$ may cause the range of $\Val$ to contain non-normal terms,
as in after applying the third substitution mentioned above,
$\Val \ec{w_1}$ is $\mu v_{\ec{w_1}}. \const{A}( \mu v_{\ec{x}}. \const{B}( \mu x_1. \const{A}( v_{\ec{x}} ) ) )$.
$\Box$
\end{example}

>>>>

To construct a completion of $\Val$, we must choose values for the free variables of $\Val$, $v_{\ec{x}}$ and $v_{\ec{w_3}}$.
The content of the set $\mathcal{T}^\M_{v_{\ec{x}}}( \Val )$ is $\alpha$-equivalent to:
\[%\begin{array}{c}
\{
\mu x. \const{A}( \mu y. \const{B}( x )),
\mu x. \const{A}( \mu y. \const{B}( y )),
\mu x. \const{B}( x ),
\mu x. \const{C}( \mu y. \const{A}( x )),
\mu x. \const{A}( \mu y. \const{C}( x )),
\mu x. \const{A}( x )
\}
%\end{array}
\]
Now, consider a model $\M$ that interprets variables in $\Ec$ based on the mapping $\Val$,
for instance, $x$ is interpretted as $\Val \ec{x}$, $y_1$ as $\Val \ec{y_1}$ and so on.
Assigning a value for $v_{\ec{x}}$ that is $\alpha$-equivalent to a value in $\mathcal{T}^\M_{v_{\ec{x}}}( \Val )$
may cause values in the range of $\Val$ to become $\alpha$-equivalent, 
which in turn may cause $\M$ to be inconsistent.
For instance, say we assign $\mu v_{\ec{x}}. \const{B}( v_{\ec{x}} )$ for $v_{\ec{x}}$.
After this substitution, $\Val \ec{y_2}$ is $\mu v_{\ec{y_2}}. \const{B}( \mu v_{\ec{x}}. \const{B}( v_{\ec{x}} ) )$, 
which has normal form $\mu v_{\ec{y_2}}. \const{B}( v_{\ec{y_2}} )$,
which is $\alpha$-equivalent to $\mu v_{\ec{x}}. \const{B}( v_{\ec{x}} )$.
However, this contradicts the disequality $x \not\teq y_2$ in $\Ec$.
Inversely, if the value assigned to $v_{\ec{x}}$ is not $\alpha$-equivalent to any term in $\mathcal{T}^\M_{v_{\ec{x}}}( \Val )$,
then the values in the range of $\Val$ remain $\alpha$-disequivalent.
For instance, we may assign values such as 
$\mu v_{\ec{x}}. \const{C}( v_{\ec{x}} )$,
$\mu v_{\ec{x}}. \const{C}( \mu x_1. \const{A}( x_1) )$, and
$\mu v_{\ec{x}}. \const{B}( \mu x_1. \const{A}( v_{\ec{x}} ) )$
to $v_{\ec{x}}$.
Notice that legal substitutions for $v_{\ec{x}}$ may cause the range of $\Val$ to contain non-normal terms,
as in after applying the third substitution mentioned above,
$\Val \ec{w_1}$ is $\mu v_{\ec{w_1}}. \const{A}( \mu v_{\ec{x}}. \const{B}( \mu x_1. \const{A}( v_{\ec{x}} ) ) )$.
$\Box$
\end{example}
